%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Semal Shastri} \\ \vspace{1pt}
     Barrie, Ontario  \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +1 249-989-5324 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{semalshastri02@gmail.com}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/semalshastri}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/vaderSame}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgian College}{Sep. 2022 -- August 2023}
      {Post Graduate Diploma in Artificial Intelligence}{Barrie, Ontario}
      \resumeSubheading
      {Ganpat University}{Sep. 2018 -- May 2022}
      {Bachelor of Information and Communication Technology}{Mehsana, Gujarat}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Simcoe County}{December 2023 -- Present}
      {Capstone Project}{Barrie, ON}
      \resumeItemListStart
        \resumeItem{Spearheaded the integration of AI, championing the county health department's initiative to elevate service quality by strategically utilizing advanced AI capabilities, fostering collaboration and innovation.}
        \resumeItem{Led data modeling efforts, meticulously analyzing historical call data to formulate a robust predictive model for dispatch calls.}
        \resumeItem{ Pioneered developing and implementing a predictive model for emergency calls, setting crucial project objectives, and skillfully incorporating demographic shifts across various cities and townships in Simcoe County. }
      \resumeItemListEnd

    \resumeSubheading
      {Polyxer Systems}{February 2022 -- August 2023}
      {Full Stack Developer}{Ahmedabad, India}
      \resumeItemListStart
        \resumeItem{Implemented Entity Framework with LINQ for efficient data access and developing RESTful APIs, driving system functionality and fostering innovation.}
        \resumeItem{ Leveraged diverse database designs and normalization techniques to develop efficient stored procedures, user-defined functions, and strategic implementation of caching mechanisms, achieving significant efficiency gains.}
        \resumeItem{Led a dynamic 5+ developer team in close collaboration with clients, ensuring a deep understanding of requirements and facilitating the timely and budget-conscious delivery of optimal solutions to meet client needs.}
      \resumeItemListEnd  
      
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Netflix IMDB analysis} $|$ \emph{Talend, MSQL, PowerBI, Report Builder}}{December 2023}
          \resumeItemListStart
            \resumeItem{Performed explanatory analysis of Netflix and IMDb datasets using MS SQL Server, employing Talend for seamless data extraction, transformation, and loading (ETL) processes.}
            \resumeItem{Established a robust data pipeline, harnessing the power of PowerBI for visualizations and insights, resulting in enhanced decision-making and strategic planning.}
            \resumeItem{Applied advanced querying and data modeling techniques in MS SQL Server to uncover key insights, enabling data-driven decision-making and contributing to optimizing content delivery strategies.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Automatic Attendance System} $|$ \emph{Python, OpenCV, dlib}}{November 2023}
          \resumeItemListStart
            \resumeItem{Deployed a robust system capable of efficiently marking student attendance by leveraging facial detection and recognition algorithms}
            \resumeItem{Developed a sophisticated solution that utilizes a collected database of facial images to identify and mark student attendance seamlessly.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Restaurant Reservation Bot} $|$ \emph{Python, Render, Google Cloud Console , Github}}{October 2023}
          \resumeItemListStart
            \resumeItem{Engineered an AI chatbot, "RestroBud," using Google Dialogflow for streamlined restaurant inquiries, leveraging Dialogflow's intent recognition and entity extraction.}
            \resumeItem{Executed a Flask-based web API to establish a seamless communication channel between the user interface and the backend logic. }
            \resumeItem{Integrated Google Cloud services to fortify RestroBud's functionality, utilizing cloud-based resources for efficient data processing and storage.}
            \resumeItem{Elevating deployment efficiency through automated deploys from Git using the Render platform, embracing a continuous integration and delivery (CI/CD) approach for code reliability and rapid updates.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: Python, Java, C, C++, C\#,  HTML/CSS, JavaScript, SQL} \\
     \textbf{Libraries}{: Keras, MatPlotLib, PyTorch, SeaBorn Numpy, Pandas, Tensorflow } \\
     \textbf{Frameworks \& Tools}{: DOTNET, NodeJS ,ReactJS ,Git, RestAPI } \\
     \textbf{Databases}{: MySQL, Apache Cassandra, SQLite, PostgreSQL} \\
    }}
 \end{itemize}
 \vspace{-16pt}

 %-----------INVOLVEMENT---------------
\section{Certifications}
            \resumeItemListStart
                \resumeItem{Python for Data Science and Machine Learning Bootcamp - Udemy}
                \resumeItem{Complete Tensorflow 2 and Keras Deep Learning Bootcamp - Udemy}
            \resumeItemListEnd
\end{document}
